### 2017-05-30 paper.tex
Merging DOI provider links

%% Include all macros below
\newcommand{\fixme}[2]{\textsc{\textbf{{#1}: {#2}}}}
\newcommand{\recommend}[1]{\textit{#1}}
\newcommand{\withurl}[2]{{#1}\footnote{\texttt{#2}}}
\newcommand{\rulemajor}[1]{\section{#1}}
\begin{document}
\vspace*{0.2in}

@@

The traditional academic system has limited ways of recognizing contributions.
Until systems have been expanded to improve this,
it is important to publish your lessons using a mechanism that provides recognition to the contributors.
Currently an effective way to do this is
to publish lessons with a DOI supplied by providers such as Zenodo\footnote{\url{https://zenodo.org/}} or DataCite\footnote{\url{https://zenodo.org/}}.
Contributors can be listed as authors
and the maintainers of the lesson as editors
to provide differentiated recognition of their contributions.

>>>>

%% Include all macros below
\newcommand{\rulemajor}[1]{\section{#1}}
\begin{document}
\vspace*{0.2in}

@@

The traditional academic system has limited ways of recognizing contributions.
Until systems have been expanded to improve this,
it is important to publish your lessons using a mechanism that provides recognition to the contributors.
Currently an effective way to do this is
to publish lessons with a DOI supplied by providers such as Zenodo (\url{https://zenodo.org/})
or DataCite (\url{https://zenodo.org/}).
Contributors can be listed as authors
and the maintainers of the lesson as editors
to provide differentiated recognition of their contributions.
